%-------------------------
% Resume in Latex — canonical template for tailored resumes
% Fill the SLOT markers with content from tailored-resume.md.
% Do not change the preamble, custom commands, spacing, or section order.
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.05in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\sloppy
\setlength{\emergencystretch}{3em}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-9pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-10pt}]

\pdfgentounicode=1

%--- CUSTOM COMMANDS ---
\newcommand{\resumeItem}[1]{
  \item\small{#1\vspace{-3pt}}
}

\newcommand{\resumeStack}[1]{
  \vspace{1pt}\item\small{\textit{#1}}\vspace{-6pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-9pt}
}
\newcommand{\resumeExpHeading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large #1} $|$ #2 & \textit{\large #3} \\
       & \text{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, label=$\bullet$]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Khushi Talaviya} \\ \vspace{2pt}
    \vspace{4pt}
    \small
    New York City, NY $|$
    \href{mailto:khushitalaviya0912@gmail.com}{khushitalaviya0912@gmail.com} $|$
    \href{https://www.linkedin.com/in/khushitalaviya/}{linkedin.com/in/khushitalaviya} $|$
    \href{https://github.com/talaviyakhushi}{github.com/talaviyakhushi}
\end{center}

%-----------SUMMARY-----------
\section{SUMMARY}
\vspace{5pt}
\small{Software engineer with a completed M.S. in Computer Science, proficient in Java, Python, and TypeScript. Shipped production features across NestJS, Spring Boot, and Angular systems, including a GenAI pricing tool and a distributed document-search platform. Comfortable owning work end to end: API design, database schema changes, cloud deployment, and CI/CD pipelines.}

%-----------SKILLS-----------
\vspace{2pt}
\section{SKILLS}
\vspace{5pt}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{Languages}{: Java, Python, TypeScript, JavaScript, SQL} \\
\textbf{Frameworks}{: Spring Boot, NestJS, Angular, Node.js} \\
\textbf{Databases}{: MySQL, PostgreSQL, MongoDB, AWS RDS} \\
\textbf{Cloud \& DevOps}{: AWS (EC2, S3, Amplify), Docker, GitHub Actions, CI/CD, Git} \\
\textbf{Practices}{: Agile/Scrum, REST and GraphQL API design, unit and integration testing (JUnit)}
}}
\end{itemize}
\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{PROFESSIONAL EXPERIENCE}
\resumeSubHeadingListStart
\vspace{10pt}
\resumeExpHeading
{Forty7}{Software Developer Co-op}{New York, NY}{Jan 2026 -- May 2026}
\vspace{-13pt}
\resumeStack{NestJS, GraphQL, TypeORM, Bull queue, AWS (EC2, S3), GitHub Actions CI/CD, gpt-4o vision}
\resumeItemListStart
  \resumeItem{Delivered a production proxy-bidding feature live across 15 lots by building a NestJS GraphQL API, TypeORM entity, and Bull queue resolution job.}
  \resumeItem{Reached 90\% pricing accuracy across 3,000+ items by building a GenAI pricing tool with gpt-4o vision, deployed to AWS EC2 via GitHub Actions CI/CD.}
  \resumeItem{Fixed silent duplicate-signup failures for a 100-user auction platform by handling failed API responses and rerouting existing profiles in a NestJS integration.}
\resumeItemListEnd
\vspace{10pt}
\resumeExpHeading
{New Jersey Institute of Technology (NJIT)}{Research Assistant}{Newark, NJ}{Apr 2025 -- Sep 2025}
\vspace{-13pt}
\resumeStack{Angular, Java, Spring Boot, REST APIs, Maven}
\resumeItemListStart
  \resumeItem{Enabled distributed document search across 4 servers by building 10+ REST endpoints in Spring Boot for a published document-outsourcing research system.}
  \resumeItem{Built a full Angular dashboard from scratch, including session-based file visibility that auto-expires in 30 minutes to prevent persistent plaintext exposure.}
  \resumeItem{Contributed to research validated at 500K-document scale by designing the client-keyword access control and search UI for the outsourcing system.}
\resumeItemListEnd
\vspace{10pt}
\resumeExpHeading
{BNP Paribas}{Software Engineer Intern}{Mumbai, India}{Jan 2024 -- Jul 2024}
\vspace{-13pt}
\resumeStack{Java, Spring Boot, Angular, REST APIs, Maven, Git, JUnit, Agile/Scrum}
\resumeItemListStart
  \resumeItem{Migrated legacy C/.NET risk logic to Java Spring Boot by delivering 10-12 Jiras with unit and integration test coverage over 5 months.}
  \resumeItem{Eliminated manual sprint reporting for a 12-person team by building a Jira-tracking tool end to end with Spring Boot REST APIs and Angular.}
  \resumeItem{Delivered Angular frontend and CSS fixes across 10-12 Jiras in Agile sprints, each shipped with JUnit unit and integration tests.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\vspace{-3pt}
\section{PROJECTS}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Outfitted - AI Personal Styling Assistant} $|$ \href{https://github.com/talaviyakhushi/outfitted}{Link}}{Mar 2026 -- present}
\vspace{-9pt}
\resumeStack{React, FastAPI, PostgreSQL (pgvector), OpenAI API (gpt-4o, gpt-4o-mini, text-embedding-3-small)}
\resumeItemListStart
  \resumeItem{Built an AI wardrobe assistant that recommends outfits from photos of a user's own clothes, tested by 10 users with 500+ items.}
  \resumeItem{Improved outfit-suggestion relevance by building a RAG retrieval pipeline with pgvector similarity search across top-20 wardrobe matches per request.}
  \resumeItem{Combined four OpenAI models, vision tagging, intent classification, chat, and embeddings, in one pipeline streaming structured outfit responses through FastAPI and React.}
\resumeItemListEnd

\resumeSubHeadingListEnd
%-----------EDUCATION-----------
\vspace{-3pt}
\section{EDUCATION}
\vspace{1pt}
\resumeSubHeadingListStart
\vspace{5pt}
\resumeSubheading
{New Jersey Institute of Technology}{May 2026}
{Master of Science in Computer Science $|$ GPA: 3.8}{Newark, NJ}
\resumeSubHeadingListEnd

\end{document}
