%-------------------------
% Resume in Latex — canonical template for tailored resumes
% Fill the SLOT markers with content from tailored-resume.md.
% Do not change the preamble, custom commands, spacing, or section order.
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.05in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\sloppy
\setlength{\emergencystretch}{3em}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-9pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-10pt}]

\pdfgentounicode=1

%--- CUSTOM COMMANDS ---
\newcommand{\resumeItem}[1]{
  \item\small{#1\vspace{-3pt}}
}

\newcommand{\resumeStack}[1]{
  \vspace{1pt}\item\small{\textit{#1}}\vspace{-6pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-9pt}
}
\newcommand{\resumeExpHeading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large #1} $|$ #2 & \textit{\large #3} \\
       & \text{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, label=$\bullet$]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Khushi Talaviya} \\ \vspace{2pt}
    \vspace{4pt}
    \small
    New York City, NY $|$
    \href{mailto:khushitalaviya0912@gmail.com}{khushitalaviya0912@gmail.com} $|$
    \href{https://www.linkedin.com/in/khushitalaviya/}{linkedin.com/in/khushitalaviya} $|$
    \href{https://github.com/talaviyakhushi}{github.com/talaviyakhushi}
\end{center}

%-----------SUMMARY-----------
\section{SUMMARY}
\vspace{5pt}
\small{Full-stack software engineer with an M.S. in Computer Science, working in Java, Python, TypeScript, Spring Boot, NestJS, React, and Angular. Shipped production features on a live auction platform, contributed to published research software, and built GenAI applications using OpenAI APIs and RAG pipelines. Picks up existing codebases fast, writes tested code, and turns guidance into working software.}

%-----------SKILLS-----------
\vspace{2pt}
\section{SKILLS}
\vspace{5pt}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{Languages}{: Java, Python, TypeScript, JavaScript, SQL} \\
\textbf{AI/ML}{: OpenAI API (gpt-4o, gpt-4o-mini, text-embedding-3-small), RAG pipelines, vector embeddings, prompt engineering} \\
\textbf{Frameworks}{: Spring Boot, NestJS, React, Angular, FastAPI, Node.js} \\
\textbf{Databases}{: PostgreSQL, MySQL, MongoDB, AWS RDS} \\
\textbf{Cloud/DevOps \& Practices}{: AWS (EC2, S3, Amplify), Docker, GitHub Actions, CI/CD, Agile/Scrum, REST and GraphQL API design}
}}
\end{itemize}
\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{PROFESSIONAL EXPERIENCE}
\resumeSubHeadingListStart
\vspace{10pt}
\resumeExpHeading
{Forty7}{Software Developer Co-op}{New York, NY}{Jan 2026 -- May 2026}
\vspace{-13pt}
\resumeStack{NestJS, Angular, AWS, OpenAI (gpt-4o)}
\resumeItemListStart
  \resumeItem{Reached 90\% pricing accuracy benchmarking gpt-4o vision estimates against 3,000+ luxury resale listings, powering a live AI pricing tool used by 100 people.}
  \resumeItem{Built a proxy bidding system end-to-end across a NestJS/GraphQL API and Angular UI, live across 15 lots in production auctions.}
  \resumeItem{Automated deployment with a GitHub Actions CI/CD pipeline to AWS EC2 and Amplify, and fixed backend integrations across a production NestJS/GraphQL API.}
\resumeItemListEnd
\vspace{10pt}
\resumeExpHeading
{New Jersey Institute of Technology (NJIT)}{Research Assistant}{Newark, NJ}{Apr 2025 -- Sep 2025}
\vspace{-13pt}
\resumeStack{Angular, Java, Spring Boot, REST APIs}
\resumeItemListStart
  \resumeItem{Enabled client-controlled document search by building a full Angular dashboard and 10+ Spring Boot REST endpoints for a published research system.}
  \resumeItem{Secured per-client document access by designing a keyword-based access control matrix for a system distributing files across 4 servers.}
  \resumeItem{Prevented stale-file exposure by adding session-based visibility that auto-expires uploads after 30 minutes in the client search interface.}
\resumeItemListEnd
\vspace{10pt}
\resumeExpHeading
{BNP Paribas}{Software Engineer Intern}{Mumbai, India}{Jan 2024 -- Jul 2024}
\vspace{-13pt}
\resumeStack{Java, Spring Boot, Angular, JUnit}
\resumeItemListStart
  \resumeItem{Centralized daily activity logging for a 12-person team by building a Jira tracker end-to-end with Spring Boot REST APIs and an Angular frontend.}
  \resumeItem{Delivered 10-12 Jiras across Java Spring Boot backend logic, Angular frontend, and CSS fixes during a legacy C/.NET to Java migration.}
  \resumeItem{Shipped every change with unit and integration test coverage across 5 months of Agile sprint delivery, following code review and documentation practices.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\vspace{-3pt}
\section{PROJECTS}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Outfitted - AI Personal Styling Assistant} $|$ \href{https://github.com/talaviyakhushi/outfitted}{Link}}{Mar 2026 -- present}
\vspace{-9pt}
\resumeStack{React, FastAPI, OpenAI (gpt-4o), pgvector}
\resumeItemListStart
  \resumeItem{Built an AI wardrobe assistant that auto-classifies clothing photos and suggests outfits via a gpt-4o and RAG-powered chat interface, tested by 10 users.}
  \resumeItem{Combined four OpenAI models for classification, intent extraction, and retrieval, indexing 500+ wardrobe items with pgvector semantic search.}
  \resumeItem{Prevented thin outfit recommendations by adding category gap-fill and full-wardrobe fallback logic when semantic retrieval under-matched.}
\resumeItemListEnd

\resumeSubHeadingListEnd
%-----------EDUCATION-----------
\vspace{-3pt}
\section{EDUCATION}
\vspace{1pt}
\resumeSubHeadingListStart
\vspace{5pt}
\resumeSubheading
{New Jersey Institute of Technology}{May 2026}
{Master of Science in Computer Science $|$ GPA: 3.8}{Newark, NJ}
\resumeSubHeadingListEnd

\end{document}
