%-------------------------
% Resume in Latex — canonical template for tailored resumes
% Fill the SLOT markers with content from tailored-resume.md.
% Do not change the preamble, custom commands, spacing, or section order.
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.05in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\sloppy
\setlength{\emergencystretch}{3em}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-9pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-10pt}]

\pdfgentounicode=1

%--- CUSTOM COMMANDS ---
\newcommand{\resumeItem}[1]{
  \item\small{#1\vspace{-3pt}}
}

\newcommand{\resumeStack}[1]{
  \vspace{1pt}\item\small{\textit{#1}}\vspace{-6pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-9pt}
}
\newcommand{\resumeExpHeading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large #1} $|$ #2 & \textit{\large #3} \\
       & \text{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, label=$\bullet$]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Khushi Talaviya} \\ \vspace{2pt}
    \vspace{4pt}
    \small
    New York City, NY $|$
    \href{mailto:khushitalaviya0912@gmail.com}{khushitalaviya0912@gmail.com} $|$
    \href{https://www.linkedin.com/in/khushitalaviya/}{linkedin.com/in/khushitalaviya} $|$
    \href{https://github.com/talaviyakhushi}{github.com/talaviyakhushi}
\end{center}

%-----------SUMMARY-----------
\section{SUMMARY}
\vspace{5pt}
\small{Full-stack engineer with hands-on experience shipping AI-integrated features across backend, frontend, and cloud systems. Builds production systems end to end, from API design to user-facing interfaces, using GPT-4o and other AI tools to prototype and debug quickly. Comfortable owning ambiguous problems while collaborating with product and design teams to turn ideas into working software.}

%-----------SKILLS-----------
\vspace{2pt}
\section{SKILLS}
\vspace{5pt}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{Languages}{: Java, Python, TypeScript, JavaScript, SQL, HTML5, CSS3} \\
\textbf{Frameworks / Libraries}{: Spring Boot, NestJS, React, Angular, FastAPI, Node.js} \\
\textbf{Databases}{: MySQL, PostgreSQL, MongoDB, AWS RDS} \\
\textbf{Cloud / DevOps}{: AWS (EC2, S3, Amplify), Docker, GitHub Actions, CI/CD} \\
\textbf{Practices / Tools}{: Agile/Scrum, REST and GraphQL API design, Git, JUnit, unit and integration testing}
}}
\end{itemize}
\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{PROFESSIONAL EXPERIENCE}
\resumeSubHeadingListStart
\vspace{10pt}
\resumeExpHeading
{Forty7}{Software Developer Co-op}{New York, NY}{Jan 2026 -- May 2026}
\vspace{-13pt}
\resumeStack{GPT-4o, NestJS, GraphQL, Angular}
\resumeItemListStart
  \resumeItem{Reached 90\% pricing accuracy on 3,000+ resale items by building an AI estimator with GPT-4o vision, live in production at Forty7.}
  \resumeItem{Built a proxy bidding system end to end across Angular and NestJS for a live auction platform, shipping across 15 lots in production.}
  \resumeItem{Fixed duplicate-signup failures by rerouting existing profiles in a NestJS GraphQL API, restoring reliable subscription flow for 100 production users at Forty7.}
\resumeItemListEnd
\vspace{10pt}
\resumeExpHeading
{New Jersey Institute of Technology (NJIT)}{Research Assistant}{Newark, NJ}{Apr 2025 -- Sep 2025}
\vspace{-13pt}
\resumeStack{Angular, Java, Spring Boot, REST APIs}
\resumeItemListStart
  \resumeItem{Built a full Angular dashboard and 10+ REST endpoints for a document-outsourcing research system, enabling secure search across a 4-server distributed backend.}
  \resumeItem{Enabled privacy-preserving search by building keyword-based access control in Angular for a system later validated at 500K-document scale in published research.}
  \resumeItem{Designed drag-and-drop keyword management and client search UI in Angular, meeting an explicit visual-design requirement for the research system's usability.}
\resumeItemListEnd
\vspace{10pt}
\resumeExpHeading
{BNP Paribas}{Software Engineer Intern}{Mumbai, India}{Jan 2024 -- Jul 2024}
\vspace{-13pt}
\resumeStack{Java, Spring Boot, Git, JUnit}
\resumeItemListStart
  \resumeItem{Eliminated manual sprint reporting by building an internal Jira-tracking tool adopted by all 12 team members at BNP Paribas.}
  \resumeItem{Delivered 10-12 Jiras across backend and frontend in a legacy C/.NET-to-Java migration, each shipped with unit and integration tests.}
  \resumeItem{Practiced Agile sprint delivery for 5 months at BNP Paribas, using Git version control and JUnit testing across a legacy system migration.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\vspace{-3pt}
\section{PROJECTS}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Outfitted -- AI Personal Styling Assistant} $|$ \href{https://github.com/talaviyakhushi/outfitted}{Link}}{Mar 2026}
\vspace{-9pt}
\resumeStack{GPT-4o, FastAPI, PostgreSQL (pgvector), React}
\resumeItemListStart
  \resumeItem{Built an AI wardrobe assistant that classifies clothing photos and recommends outfits in real time, validated by 10 users who uploaded 500+ items total.}
  \resumeItem{Improved outfit-suggestion relevance by combining pgvector semantic search with intent extraction and category gap-fill logic across 4 orchestrated OpenAI models.}
  \resumeItem{Delivered real-time outfit visuals by streaming GPT-4o responses over SSE and rendering 5-slot collages matched to wardrobe photos via fuzzy text matching.}
\resumeItemListEnd

\resumeSubHeadingListEnd
%-----------EDUCATION-----------
\vspace{-3pt}
\section{EDUCATION}
\vspace{1pt}
\resumeSubHeadingListStart
\vspace{5pt}
\resumeSubheading
{New Jersey Institute of Technology}{May 2026}
{Master of Science in Computer Science}{Newark, NJ}
\resumeSubHeadingListEnd

\end{document}
