%-------------------------
% Resume in Latex — canonical template for tailored resumes
% Filled for: Amazon — Software Development Engineer - 2026 (US)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.05in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\sloppy
\setlength{\emergencystretch}{3em}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-9pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-10pt}]

\pdfgentounicode=1

%--- CUSTOM COMMANDS ---
\newcommand{\resumeItem}[1]{
  \item\small{#1\vspace{-3pt}}
}

\newcommand{\resumeStack}[1]{
  \vspace{1pt}\item\small{\textit{#1}}\vspace{-6pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-9pt}
}
\newcommand{\resumeExpHeading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large #1} $|$ #2 & \textit{\large #3} \\
       & \text{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, label=$\bullet$]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Khushi Talaviya} \\ \vspace{2pt}
    \vspace{4pt}
    \small
    New York City, NY $|$
    \href{mailto:khushitalaviya0912@gmail.com}{khushitalaviya0912@gmail.com} $|$
    \href{https://www.linkedin.com/in/khushitalaviya/}{linkedin.com/in/khushitalaviya} $|$
    \href{https://github.com/talaviyakhushi}{github.com/talaviyakhushi}
\end{center}

%-----------SUMMARY-----------
\section{SUMMARY}
\vspace{5pt}
\small{Software engineer with a completed M.S. in Computer Science and hands-on experience across Java, Python, and TypeScript. Shipped production features spanning NestJS and Spring Boot APIs, GenAI-powered tools using the OpenAI API, and AWS cloud deployments. Comfortable owning a feature's full lifecycle, from database design and REST/GraphQL APIs through CI/CD deployment and production debugging.}

%-----------SKILLS-----------
\vspace{2pt}
\section{SKILLS}
\vspace{5pt}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{Languages}{: Java, Python, TypeScript, JavaScript, SQL} \\
\textbf{AI / ML}{: OpenAI API (gpt-4o, gpt-4o-mini, text-embedding-3-small), RAG pipelines, vector embeddings} \\
\textbf{Cloud / DevOps}{: AWS (EC2, Amplify, S3), Docker, GitHub Actions, CI/CD} \\
\textbf{Databases}{: PostgreSQL, MySQL, MongoDB, AWS RDS} \\
\textbf{Frameworks \& Tools}{: Spring Boot, NestJS, Angular, React, Git, JUnit}
}}
\end{itemize}
\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{PROFESSIONAL EXPERIENCE}
\resumeSubHeadingListStart
\vspace{10pt}
\resumeExpHeading
{Forty7}{Software Developer Co-op}{New York, NY}{Jan 2026 -- May 2026}
\vspace{-13pt}
\resumeStack{NestJS, GraphQL, AWS, OpenAI API (gpt-4o)}
\resumeItemListStart
  \resumeItem{Launched a proxy bidding feature live across 15 lots in 3 auctions, resolving bid conflicts through a role-guarded GraphQL mutation.}
  \resumeItem{Reached 90\% pricing accuracy on 3,000+ items by building a gpt-4o vision pricing tool with a GitHub Actions CI/CD pipeline on AWS.}
  \resumeItem{Fixed a token-collision bug causing duplicate JWTs for concurrent logins, and resolved an NGXS auth race condition blocking route guards.}
\resumeItemListEnd
\vspace{10pt}
\resumeExpHeading
{New Jersey Institute of Technology (NJIT)}{Research Assistant}{Newark, NJ}{Apr 2025 -- Sep 2025}
\vspace{-13pt}
\resumeStack{Angular, Java, Spring Boot, REST APIs}
\resumeItemListStart
  \resumeItem{Enabled distributed document search across 4 servers by building 10+ REST endpoints in Java Spring Boot for a published research system.}
  \resumeItem{Owned the full frontend by building an Angular dashboard with session-based file visibility, keyword access control, and drag-and-drop uploads.}
  \resumeItem{Designed REST API contracts ahead of backend implementation for research later validated at 500K-document scale.}
\resumeItemListEnd
\vspace{10pt}
\resumeExpHeading
{BNP Paribas}{Software Engineer Intern}{Mumbai, India}{Jan 2024 -- Jul 2024}
\vspace{-13pt}
\resumeStack{Java, Spring Boot, Angular, Git}
\resumeItemListStart
  \resumeItem{Centralized daily Jira logging for a 12-person team by building a full-stack tracker with Spring Boot REST APIs and Angular.}
  \resumeItem{Delivered 10-12 Jiras across a Java Spring Boot migration from legacy C/.NET, each shipped with JUnit unit and integration tests.}
  \resumeItem{Practiced Agile Scrum delivery across 5 months of sprints, using Git version control for backend, frontend, and styling changes.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\vspace{-3pt}
\section{PROJECTS}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Outfitted -- AI Personal Styling Assistant} $|$ \href{https://github.com/talaviyakhushi/outfitted}{Link}}{Mar 2026 -- present}
\vspace{-9pt}
\resumeStack{OpenAI API, FastAPI, PostgreSQL (pgvector), React}
\resumeItemListStart
  \resumeItem{Built an AI wardrobe assistant tested by 10 users who uploaded 500+ clothing items, suggesting outfits via chat using OpenAI vision and vector search.}
  \resumeItem{Combined 4 OpenAI models in one pipeline by building a RAG retrieval flow with pgvector similarity search and category gap-fill logic.}
  \resumeItem{Secured user data with Supabase Auth JWT validation while building the FastAPI backend and React frontend for the full product.}
\resumeItemListEnd

\resumeSubHeadingListEnd
%-----------EDUCATION-----------
\vspace{-3pt}
\section{EDUCATION}
\vspace{1pt}
\resumeSubHeadingListStart
\vspace{5pt}
\resumeSubheading
{New Jersey Institute of Technology}{May 2026}
{Master of Science in Computer Science $|$ GPA: 3.8}{Newark, NJ}
\resumeSubHeadingListEnd

\end{document}
